Randomization Examples using `okcupiddata` `profiles` data

### 2017-10-10 docs/articles/profiles_examples.Rmd
Update pkgdown documentation

---
output:
  github_document:
    toc: true 
    toc_depth: 3
---

### Hypothesis tests
![h-test diagram](../figs/ht-diagram.png)

#### Examples

@@

@@

### Confidence intervals

>>>>

---
title: "Randomization Examples using `okcupiddata` `profiles` data"
author: "Chester Ismay"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    df_print: kable
vignette: |
  %\VignetteIndexEntry{OKCupid profiles example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 5, cache = TRUE) 
```

## Data preparation

@@

## Hypothesis tests

@@

## Confidence intervals
